---
# =============================================================================
# 📄 PDF VERSION — UNCOMMENT THIS ENTIRE BLOCK (including --- lines) FOR PDF
# =============================================================================
# ---
# title: ""
# author: ""
# date: ""
# 
# format:
#   pdf:
#     latex-engine: xelatex
#     number-sections: true
#     toc: false
#     fontsize: 12pt
#     linestretch: 1.5
#     geometry: margin=1in
#     mainfont: "Times New Roman"
#     include-before-body:
#       text: |
#         \begin{titlepage}
#           \centering
#           \vspace*{3cm}
#           {\Huge\bfseries Inter-Rater Reliability Between Human Raters \& Qwen \\[0.5cm]}
#           \vspace{2cm}
#           {\Large Emily Han \par}
#           \vspace*{3cm}
#           {\large January 27, 2025\par}
#           \thispagestyle{empty}
#         \end{titlepage}
#         \newpage
#         \pagenumbering{arabic}


# =============================================================================
# 🌐 HTML VERSION — UNCOMMENT THIS ENTIRE BLOCK (including --- lines) FOR HTML
# =============================================================================

title: "Inter-Rater Reliability Between Human Raters & Qwen"
author: "Emily Han"
date: "January 27, 2025"

format:
  html:
    toc: false
    number-sections: true
    fig-cap-location: bottom
    tbl-cap-location: top
    theme: cosmo
    css: |
      .title-block {
        text-align: center;
        padding: 2rem 0;
        border-bottom: 1px solid #eee;
        margin-bottom: 2rem;
      }
      .title-block h1 {
        font-size: 2.2rem;
        margin-bottom: 0.5rem;
        color: #2c3e50;
      }
      .title-block .author {
        font-size: 1.4rem;
        margin: 0.3rem 0;
        color: #34495e;
      }
      .title-block .date {
        font-size: 1.1rem;
        color: #7f8c8d;
      }
      
# =============================================================================    
  

execute:
  echo: false
  warning: false
  message: false
---


## Reliability Between Human Raters Within Group

```{r}
suppressMessages({
  library(dplyr)
  library(tidyr)
  library(irr)
  library(stringr)
  library(ggplot2)
  library(tidyverse)
  library(ggrepel)
  library(ggpubr)
  library(cowplot)
  library(scales)
  library(patchwork)
  library(knitr)
})
```

```{r}
# Load the datasets 

human_turn <- read.csv("human_turn.csv")
human_hol <- read.csv("human_holistic.csv")
llm_turn <- read.csv("llm_turn.csv")
llm_hol <- read.csv("llm_holistic.csv")
```

## Human Rating Within Group Reliability

explain why we specifically chose to use Krippendorff's alpha

What does the result mean?

What the result look like the way it is

```{r, Krippendorff Data Analysis}
## Human-Turn Level Rating Analysis 
### Transform the Data into Matrices

# 1) split into group_id × metric_id chunks
turn_chunks <- human_turn %>%
  mutate(item_id = paste(scenario_id, turn, metric_id, number_id, sep="__")) %>%
  select(group_id, metric_id, item_id, rater_id, score) %>%
  group_by(group_id, metric_id) %>%
  group_split()

# 2) build a matrix for each chunk
turn_mats_by_group_metric <- lapply(turn_chunks, function(gdf) {

  wide <- gdf %>%
    select(item_id, rater_id, score) %>%
    pivot_wider(names_from = rater_id, values_from = score) %>%
    arrange(item_id)

  mat <- as.matrix(wide %>% select(-item_id))
  rownames(mat) <- wide$item_id
  mat
})

# 3) name each list element using BOTH group and metric
turn_chunk_names <- lapply(turn_chunks, function(gdf) {
  paste0(unique(gdf$group_id), "_", unique(gdf$metric_id))
})

names(turn_mats_by_group_metric) <- unlist(turn_chunk_names)


### Krippendorff's Alpha Analysis for the turn-level rating
alpha_turn <- lapply(turn_mats_by_group_metric, function(mat) {
  irr::kripp.alpha(t(mat), method = "ordinal")
})


## _________________________________________________________________________ ##

## Human-Holistic Rating Analysis 
### Transform the Data into Matrices

# 1) split into group_id × metric_id chunks
hol_chunks <- human_hol %>%
  mutate(item_id = paste(scenario_id, turn, metric_id, number_id, sep="__")) %>%
  select(group_id, metric_id, item_id, rater_id, score) %>%
  group_by(group_id, metric_id) %>%
  group_split()

# 2) build a matrix for each chunk
hol_mats_by_group_metric <- lapply(hol_chunks, function(gdf) {

  wide <- gdf %>%
    select(item_id, rater_id, score) %>%
    pivot_wider(names_from = rater_id, values_from = score) %>%
    arrange(item_id)

  mat <- as.matrix(wide %>% select(-item_id))
  rownames(mat) <- wide$item_id
  mat
})

# 3) name each list element using BOTH group and metric
hol_chunk_names <- lapply(hol_chunks, function(gdf) {
  paste0(unique(gdf$group_id), "_", unique(gdf$metric_id))
})

names(hol_mats_by_group_metric) <- unlist(hol_chunk_names)


### Krippendorff's Alpha Analysis for the holistic rating
alpha_hol <- lapply(hol_mats_by_group_metric, function(mat) {
  irr::kripp.alpha(t(mat), method = "ordinal")
})

```

```{r, Result Summary DataFrame}
## Function to organize the result into a dataframe

alpha_list_to_df <- function(alpha_list, kind_label) {
  data.frame(
    group_metric = names(alpha_list),
    alpha    = sapply(alpha_list, \(x) x$value),
    subjects = sapply(alpha_list, \(x) x$subjects),
    raters   = sapply(alpha_list, \(x) x$raters),
    stringsAsFactors = FALSE
  ) %>%
    tidyr::separate(
      group_metric,
      into = c("group_id", "metric_id"),
      sep = "_",
      extra = "merge",
      fill = "right"
    ) %>%
    mutate(kind = kind_label)
}

turn_alpha_summary    <- alpha_list_to_df(alpha_turn, "Single-turn")
holistic_alpha_summary <- alpha_list_to_df(alpha_hol, "Holistic")
alpha_all <- bind_rows(turn_alpha_summary, holistic_alpha_summary)
```

```{r, Alpha Data Table}
#| label: tbl-alpha
#| tbl-cap: "Krippendorff's Alpha Values by Metric and Rater Group"
## Reordering and Remapping the Metric Var 

metric_map_full <- c(
  contextual_appropriateness = "Contextual Appropriateness",
  emotional_calibration      = "Emotional Calibration",
  emotional_escalation       = "Emotional Escalation",
  functional_empathy         = "Functional Empathy",
  tone_appropriateness       = "Tone Appropriateness",
  emotional_adaptivity       = "Emotional Adaptivity",
  problem_resolution         = "Problem Resolution",
  emotional_coherence        = "Emotional Coherence"
)

metric_order <- c(
  "Tone Appropriateness",
  "Emotional Calibration",
  "Emotional Escalation",
  "Functional Empathy",
  "Contextual Appropriateness",
  "Emotional Coherence",
  "Emotional Adaptivity",
  "Problem Resolution"
)

alpha_all <- alpha_all %>%
    mutate(
    metric_id = str_trim(metric_id),
    metric_label = dplyr::recode(metric_id, !!!metric_map_full, .default = metric_id),
    Metric = factor(metric_label, levels = metric_order),
    group_id = factor(group_id, levels = c("Group A", "Group B", "Group C"))
  )


## Create the table for the Krippendorff's alpha
alpha_table <- alpha_all %>%
  select(Metric, group_id, Alpha = alpha) %>%
  distinct() %>%
  arrange(Metric) %>%
  pivot_wider(names_from = group_id, values_from = Alpha) %>%
  mutate(across(starts_with("Group"), ~ round(.x, 3)))

kable(alpha_table)
```

```{r, Alpha HeatMap}
#| label: fig-alpha-heatmap
#| fig-cap: "Human Inter-Rater Reliability by Metric and Group"


## Create the heatmap for the Krippendorff's alpha

alpha_plot_df <- alpha_all %>%
  mutate(
    # Reverse levels so first item appears at TOP of plot
    Metric = factor(metric_label, levels = rev(metric_order)),
    group_id = factor(group_id, levels = c("Group A", "Group B", "Group C"))
  )

alpha_plot <- ggplot(alpha_plot_df, aes(x = group_id, y = Metric, fill = alpha)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(alpha, 2)), size = 3) +
  scale_fill_gradient2(
    low = "#d73027", mid = "#f7f7f7", high = "#1a9850",
    midpoint = 0.4, na.value = "grey90", name = "Krippendorff’s α"
  ) +
  labs(
    title = "Human Inter-Rater Reliability by Metric and Group",
    x = "Rater Group", y = NULL,
  ) +
  theme_pubr(base_size = 10) +
  theme(
    plot.title = element_text(
      hjust = 0.50,
      face = "bold",
      margin = margin(b = 20)
    )) +
  theme(
    axis.text.y  = element_text(size = 9.5),
    axis.title.x = element_text(size = 11, margin = margin(t = 10)),
    legend.position = "right",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9),
    legend.box.margin = margin(r = 50) 
  ) 

alpha_plot
```

## Reliability Between Human Raters Vs LLM

the things that i calculate Explain the spearman rho and what it is interpreting in general Explain the how it relates to the alingment normally and how it is in my specific case

```{r, Human-LLM Data Integration}
# Combine turn and holistic rating for both llm and human 

llm_all <- bind_rows(llm_turn, llm_hol) %>%
  mutate(kind = if_else(turn == 0, "holistic", "turn"))

human_all <- bind_rows(human_turn, human_hol) %>%
  mutate(kind = if_else(turn == 0, "holistic", "turn"))

human_item <- human_all %>%
  mutate(turn = if_else(kind == "holistic", NA_integer_, turn)) %>%
  group_by(group_id, kind, scenario_id, turn, metric_id, number_id) %>%
  summarise(
    human_median = median(score, na.rm = TRUE),
    human_var = var(score, na.rm = TRUE),
    n_humans = sum(!is.na(score)),
    human_iqr = IQR(score, na.rm = TRUE),
    .groups = "drop"
  )

llm_item <- llm_all %>%
  mutate(turn = if_else(kind == "holistic", NA_integer_, turn)) %>%
  group_by(group_id, kind, scenario_id, turn, metric_id, number_id) %>%
  summarise(
    llm_score = score[1],
    judge_model = first(judge_model),
    .groups = "drop"
  )

## Dataset with both LLM and Human Rating 
alignment_df <- human_item %>%
  left_join(
    llm_item %>% 
      select(scenario_id, turn, number_id, llm_score),
    by = c("scenario_id","turn","number_id")
  ) %>%
  mutate(
    abs_error = abs(llm_score - human_median),
    within_1  = abs_error <= 1,
    level = str_extract(scenario_id, "^L\\d+"),
    emotion = str_extract(scenario_id, "(?<=_)[a-z]+(?=_)",
    )
  )
alignment_df <- alignment_df %>%
  mutate(
    level = factor(level, levels = c("L1", "L5", "L10"))
  )
```

```{r, Score_Distribution}
#| label: tbl-score-distribution
#| tbl-cap: "Score Distribution Comparison"

# LLM distribution
llm_score_dis <- llm_all %>% 
  count(score) %>% 
  mutate(percent = n / sum(n) * 100) %>%
  mutate(score = as.character(score)) %>%
  rename(
    Score = score,
    "LLM Ratings (N)" = n,
    "LLM Ratings (%)" = percent
  )

# Human distribution
human_score_dis <- human_all %>% 
  count(score) %>% 
  mutate(percent = n / sum(n) * 100) %>%
  mutate(score = as.character(score)) %>%
  rename(
    Score = score,
    "Human Ratings (N)" = n,
    "Human Ratings (%)" = percent
  )



# Combine + fix order
combined_score_dis <- full_join(llm_score_dis, human_score_dis, by = "Score") %>%
  mutate(order = as.numeric(Score)) %>%
  arrange(order) %>%
  select(-order)


combined_score_dis <- bind_rows(
  combined_score_dis,
  tibble(
    Score = "Total Observations",
    "LLM Ratings (N)" = sum(combined_score_dis$`LLM Ratings (N)`, na.rm = TRUE),
    "LLM Ratings (%)" = NA_real_,
    "Human Ratings (N)" = sum(combined_score_dis$`Human Ratings (N)`, na.rm = TRUE),
    "Human Ratings (%)" = NA_real_
  )
)

combined_score_dis_print <- combined_score_dis %>%
  mutate(
    `LLM Ratings (%)` = ifelse(
      Score == "Total Observations" & is.na(`LLM Ratings (%)`),
      "",
      `LLM Ratings (%)`
    ),
    `Human Ratings (%)` = ifelse(
      Score == "Total Observations" & is.na(`Human Ratings (%)`),
      "",
      `Human Ratings (%)`
    )
  )

kable(
  combined_score_dis_print,
  align = "c"
)


```




### LLM & Human Alignment by Metric

```{r, Metric Data Table}
#| label: tbl-alignment-metric
#| tbl-cap: "LLM-Human Alignment Statistics by Metric"

## Data table for Alignment by Metric + Spearman Cor Test 

alignment_by_metric <- alignment_df %>%
  group_by(metric_id) %>%
  summarise(
    n = n(),
    alignment_rate = mean(within_1, na.rm = TRUE),
    MAE = mean(abs_error, na.rm = TRUE),
    Spearman_rho = cor(llm_score, human_median, method = "spearman"),
    human_score_avg = mean(human_median),
    llm_score_avg = mean(llm_score)
  )  %>%
  arrange(desc(alignment_rate)) %>%
  mutate(across(where(is.numeric) & !n, ~ round(., 3)))

alignment_by_metric <- alignment_by_metric %>%
  mutate(
    metric_id = case_when(
      metric_id %in% c("tone_appropriateness", "Tone Appropriateness") ~ "Tone Appropriateness",
      metric_id %in% c("emotional_calibration", "Emotional Calibration Accuracy") ~ "Emotional Calibration",
      metric_id %in% c("emotional_escalation") ~ "Emotional Escalation",
      metric_id %in% c("functional_empathy") ~ "Functional Empathy",
      metric_id %in% c("contextual_appropriateness") ~ "Contextual Appropriateness",
      metric_id %in% c("emotional_coherence") ~ "Emotional Coherence",
      metric_id %in% c("emotional_adaptivity") ~ "Emotional Adaptivity",
      metric_id %in% c("problem_resolution") ~ "Problem Resolution",
      TRUE ~ metric_id
    )
  )

alignment_by_metric <- alignment_by_metric %>%
  mutate(
    metric_id = factor(metric_id, levels = metric_order, ordered = TRUE)
  ) %>%
  arrange(metric_id)

kable(alignment_by_metric)
```

```{r, Metric Plot}
#| label: fig-metric-alignment
#| fig-cap: "LLM–Human Alignment by Metric"

## Plot Alignment by Metric

plot_df <- alignment_by_metric %>%
  mutate(
    # Reverse levels so first item appears at TOP of plot
    Metric = factor(metric_id, levels = rev(metric_order))
  )

p_align <- ggplot(plot_df, aes(x = Metric, y = alignment_rate)) +
  geom_col(fill = "#4C72B0") +
  geom_text(
    aes(label = scales::percent(alignment_rate, accuracy = 1)),
    hjust = -0.1,
    size = 3
  ) +
  scale_y_continuous(
    labels = scales::percent,
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip() +
  labs(x = NULL, y = "Alignment Rate (±1 on 5-point scale)") +
  theme_pubr(base_size = 10) +
  theme(
    axis.text.y  = element_text(size = 10.5, margin = margin(r = 10)),
    axis.title.x = element_text(size = 11, margin = margin(t = 10))
  )

# 3) Right plot: MAE (hide Metric labels + keep your margins)
p_mae <- ggplot(plot_df, aes(x = Metric, y = MAE)) +
  geom_col(fill = "#DD8452") +
  geom_text(
    aes(label = round(MAE, 2)),
    nudge_y = 0.03,
    hjust = 0,
    size = 3
  ) +
  scale_y_continuous(
    limits = c(0, max(plot_df$MAE, na.rm = TRUE) * 1.20),
    expand = expansion(mult = c(0, 0.02))
  ) +
  coord_flip(clip = "off") +
  labs(x = NULL, y = "MAE (1–5 scale)") +
  theme_pubr(base_size = 10) +
  theme(
    plot.margin = margin(10, 30, 10, 10),     # keep your right-margin for labels
    axis.text.y  = element_blank(),           # ✅ don't show Metric labels twice
    axis.title.y = element_blank(),           # ✅ remove duplicated axis title on left side
    axis.ticks.y = element_blank(),           # optional: cleaner
    axis.title.x = element_text(size = 11, margin = margin(t = 10))
  )

# 4) Combine side-by-side with ONE centered title for both
metric_side_by_side <-
  wrap_plots(
    p_align,
    plot_spacer(),   # 👈 creates space
    p_mae,
    ncol = 3,
    widths = c(1, 0.08, 1)  # middle = gap size
  ) +
  plot_annotation(
    title = "LLM–Human Alignment by Metric"
  ) &
  theme(
    plot.title = element_text(
      hjust = 0.75,
      face = "bold",
      margin = margin(b = 12)
    )
  )

metric_side_by_side

```

### LLM & Human Alignment by Scenario

```{r, Scenario Data Table}
#| label: tbl-alignment-scenario
#| tbl-cap: "LLM-Human Alignment Statistics by Scenario"


## Data table for Alignment by Scenario + Spearman Cor Test 

alignment_by_scenario <- alignment_df %>%
  group_by(level, emotion) %>%
  summarise(alignment_rate = mean(within_1),
            Avg_Var = mean(human_var),
            Spearman_rho = cor(llm_score, human_median, method = "spearman"),
            MAE = mean(abs_error, na.rm = TRUE)
            )

kable(alignment_by_scenario)
```

```{r, Scenario Plot}
#| label: fig-scenario-alignment
#| fig-cap: "LLM–Human Alignment by Scenario"


## Plot Alignment by Scenario
plot_scenario <- alignment_by_scenario %>%
  mutate(
    emotion = factor(str_to_title(emotion), 
                    levels = c("Neutral", "Frustrated", "Angry")),
    level = factor(level, levels = c("L10", "L5", "L1")),
    Scenario = paste0(level, " ", emotion)
  ) %>%
  arrange(emotion, level) %>%
  mutate(Scenario = factor(Scenario, levels = rev(unique(Scenario))))

# Left plot: Alignment Rate
p_scenario_align <- ggplot(plot_scenario, aes(x = alignment_rate, y = Scenario, fill = emotion)) +
  geom_col() +
  geom_text(aes(label = scales::percent(alignment_rate, accuracy = 1)), 
            hjust = -0.1, size = 3) +
  scale_fill_manual(values = c("Neutral" = "#2ECC71",
                                "Frustrated" = "#F39C12",
                                "Angry" = "#E74C3C")) +
  scale_x_continuous(labels = scales::percent, 
                     limits = c(0, 1), 
                     expand = expansion(mult = c(0, 0.05))) +
  coord_cartesian(clip = "off") +
  labs(x = "Alignment Rate (±1 on 5-point scale)", y = NULL) +
  theme_pubr(base_size = 10) +
  theme(
    axis.text.y = element_text(size = 10.5, margin = margin(r = 10)),
    axis.title.x = element_text(size = 11, margin = margin(t = 10)),
    legend.position = "none"
  )

# Right plot: MAE
p_scenario_mae <- ggplot(plot_scenario, aes(x = MAE, y = Scenario, fill = emotion)) +
  geom_col() +
  geom_text(aes(label = round(MAE, 2)),
            hjust = -0.1,
            size = 3) +
  scale_fill_manual(values = c("Neutral" = "#2ECC71",
                                "Frustrated" = "#F39C12",
                                "Angry" = "#E74C3C")) +
  scale_x_continuous(limits = c(0, max(plot_scenario$MAE, na.rm = TRUE) * 1.20),
                     expand = expansion(mult = c(0, 0.02))) +
  labs(x = "MAE (1–5 scale)", y = NULL) +
  theme_pubr(base_size = 10) +
  theme(
    plot.margin = margin(10, 30, 10, 20),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_text(size = 11, margin = margin(t = 10)),
    legend.position = "bottom",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 9),
    legend.box.margin = margin(r = 50) 
  )

# Combine side-by-side
scenario_side_by_side <-
  wrap_plots(
    p_scenario_align,
    plot_spacer(),
    p_scenario_mae,
    ncol = 3,
    widths = c(1, 0.08, 1)
  ) +
  plot_annotation(
    title = "LLM–Human Alignment by Scenario"
  ) &
  theme(
    plot.title = element_text(
      hjust = 0.50,
      face = "bold",
      margin = margin(b = 12)
    )
  )

scenario_side_by_side
```

### LLM & Human Alignment Broken Down to Emotion & Topic Intensity

```{r, Emotion Data Table}
#| label: tbl-alignment-emotion
#| tbl-cap: "LLM-Human Alignment Statistics by Emotion"
#| 
alignment_by_level <- alignment_df %>%
  group_by(level) %>%
  summarise(alignment_rate = mean(within_1), 
            Spearman_rho = cor(llm_score, human_median, method = "spearman"),
            MAE = mean(abs_error, na.rm = TRUE)
            )

alignment_by_emotion <- alignment_df %>%
  group_by(emotion) %>%
  summarise(alignment_rate = mean(within_1), 
            Spearman_rho = cor(llm_score, human_median, method = "spearman"),
            MAE = mean(abs_error, na.rm = TRUE)
            )


kable(alignment_by_level)
```


```{r, Intensity Data Table}
#| label: tbl-alignment-intensity
#| tbl-cap: "LLM-Human Alignment Statistics by Topic Intensity"

kable(alignment_by_emotion)
```

```{r, Emotion Plot}
#| label: fig-emotion-alignment
#| fig-cap: "LLM–Human Alignment by Emotion"

## Plot Alignment by Emotion


plot_emotion <- alignment_by_emotion %>%
  mutate(
    emotion = recode(
      emotion,
      "neutral" = "Neutral",
      "angry" = "Angry",
      "frustrated" = "Frustrated"
    ))



p_emotion_align <- ggplot(plot_emotion, aes(x = emotion, y = alignment_rate)) +
  geom_col(fill = "#4C72B0",  width = 0.7) +
  geom_text(
    aes(label = scales::percent(alignment_rate, accuracy = 1)),
    hjust = -0.1,
    size = 3
  ) +
  scale_y_continuous(
    labels = scales::percent,
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip() +
  labs(x = NULL, y = "Alignment Rate (±1 on 5-point scale)") +
  theme_pubr(base_size = 10) +
  theme(
    axis.text.y  = element_text(size = 10.5, margin = margin(r = 10)),
    axis.title.x = element_text(size = 11, margin = margin(t = 10))
  )

# 3) Right plot: MAE (hide Emotion labels + keep your margins)
p_emotion_mae <- ggplot(plot_emotion, aes(x = emotion, y = MAE)) +
  geom_col(fill = "#DD8452",  width = 0.7) +
  geom_text(
    aes(label = round(MAE, 2)),
    nudge_y = 0.03,
    hjust = 0,
    size = 3
  ) +
  scale_y_continuous(
    limits = c(0, max(plot_emotion$MAE, na.rm = TRUE) * 1.20),
    expand = expansion(mult = c(0, 0.02))
  ) +
  coord_flip(clip = "off") +
  labs(x = NULL, y = "MAE (1–5 scale)") +
  theme_pubr(base_size = 10) +
  theme(
    plot.margin = margin(10, 30, 10, 10),     # keep your right-margin for labels
    axis.text.y  = element_blank(),           # ✅ don't show Metric labels twice
    axis.title.y = element_blank(),           # ✅ remove duplicated axis title on left side
    axis.ticks.y = element_blank(),           # optional: cleaner
    axis.title.x = element_text(size = 11, margin = margin(t = 10))
  )

# 4) Combine side-by-side with ONE centered title for both
emotion_side_by_side <-
  wrap_plots(
    p_emotion_align,
    plot_spacer(),   # 👈 creates space
    p_emotion_mae,
    ncol = 3,
    widths = c(1, 0.08, 1)  # middle = gap size
  ) +
  plot_annotation(
    title = "LLM–Human Alignment by Emotion"
  ) &
  theme(
    plot.title = element_text(
      hjust = 0.50,
      face = "bold",
      margin = margin(b = 12)
    )
  )

emotion_side_by_side
```

```{r, Topic Sensitivity Plot}
#| label: fig-level-alignment
#| fig-cap: "LLM–Human Alignment by Topic Sensitivity"

## Plot Alignment by Level (Topic Sensitivity)
plot_level <- alignment_by_level %>%
  mutate(
    level = recode(
      level,
      "L1" = "Low Sensitivity (L1)",
      "L5" = "Medium Sensitivity (L5)",
      "L10" = "High Sensitivity (L10)"
    ),
    level = factor(level, levels = c("High Sensitivity (L10)", "Medium Sensitivity (L5)", "Low Sensitivity (L1)"))
  )

# Left plot: Alignment Rate
p_level_align <- ggplot(plot_level, aes(x = level, y = alignment_rate)) +
  geom_col(fill = "#4C72B0",  width = 0.7) +
  geom_text(
    aes(label = scales::percent(alignment_rate, accuracy = 1)),
    hjust = -0.1,
    size = 3
  ) +
  scale_y_continuous(
    labels = scales::percent,
    limits = c(0, 1),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip(clip = "off") +
  labs(x = NULL, y = "Alignment Rate (±1 on 5-point scale)") +
  theme_pubr(base_size = 10) +
  theme(
    plot.margin = margin(10, 30, 10, 10),
    axis.text.y = element_text(size = 10.5, margin = margin(r = 10)),
    axis.title.x = element_text(size = 11, margin = margin(t = 10))
  )

# Right plot: MAE
p_level_mae <- ggplot(plot_level, aes(x = level, y = MAE)) +
  geom_col(fill = "#DD8452", width = 0.7) + 
  geom_text(
    aes(label = round(MAE, 2)),
    nudge_y = 0.03,
    hjust = 0,
    size = 3
  ) +
  scale_y_continuous(
    limits = c(0, max(plot_level$MAE, na.rm = TRUE) * 1.20),
    expand = expansion(mult = c(0, 0.02))
  ) +
  coord_flip(clip = "off") +
  labs(x = NULL, y = "MAE (1–5 scale)") +
  theme_pubr(base_size = 10) +
  theme(
    plot.margin = margin(10, 30, 10, 10),
    axis.text.y = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_text(size = 11, margin = margin(t = 10))
  )

# Combine side-by-side
level_side_by_side <-
  wrap_plots(
    p_level_align,
    plot_spacer(),
    p_level_mae,
    ncol = 3,
    widths = c(1, 0.08, 1)
  ) +
  plot_annotation(
    title = "LLM–Human Alignment by Topic Sensitivity"
  ) &
  theme(
    plot.title = element_text(
      hjust = 0.50,
      face = "bold",
      margin = margin(b = 12)
    )
  )

level_side_by_side
```














